Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward

### 2022-07-02 analysis/paper/paper.Rmd
Spellcheck and reknit

We fitted Bayesian logistic mixed models (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000 and thinning of 1) using cumulative family function with a logit link for ordinal data using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021].
The cumulative family allows for the probability of a given value is the probability of that value or any smaller value.
Priors were selected to be weakly informative and deemed suitable through using `pp_check()` to examine the the models' predictions based on priors only (using the parameter `sample_prior = only` in `brm()`).
Priors over all parameters were set as: normal (mean = 0.00, SD = 1.0) distributions for both fixed parameters and random effects.
The best fitting models were selected by using Widely Applicable Information Criterion (WAIC) and the expected log pointwise predictive density via `loo_compare()`.

@@

The authors are grateful for insightful comments from Dr. David Ferris and the USQ Centre for Crop Health Advisory Group on the final manuscript, from Ms. Anna Hepworth for statistical guidance on evaluating inter-rater scores and Dr Rebecca O'Leary for her insightful comments that helped improve the paper.

@@

tab_t %>%
  rowwise() %>%
  mutate(Total = sum(c_across(where(is.numeric)), na.rm = T)) %>%
  arrange(desc(Total)) %>%
  rename(Software = software_used) %>% 
  flextable() %>%
  autofit() %>%
  set_caption(
    "The frequency of use of top ten sofware programs by year of publication that were found to be used in the papers that were surveyed."
  )
```

>>>>

We fitted Bayesian logistic mixed models (estimated using MCMC sampling with 4 chains of 10000 iterations and a warm-up of 5000 and thinning of 1) using cumulative family function with a logit link for ordinal data using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021].
The cumulative family allows for the probability of a given value is the probability of that value or any smaller value.
Priors were selected to be weakly informative and deemed suitable through using `pp_check()` to examine the the models' predictions based on priors only (using the parameter `sample_prior = only` in `brm()`).
Priors over all parameters were set as: normal (mean = 0.00, SD = 1.0) distributions for both fixed parameters and random effects.
The best fitting models were selected by using Widely Applicable Information Criterion (WAIC) and the expected log point-wise predictive density via `loo_compare()`.

@@

The authors are grateful for insightful comments from Dr. David Ferris and the USQ Centre for Crop Health Advisory Group on the final manuscript, from Ms. Anna Hepworth for statistical guidance on evaluating inter-rater scores and Dr. Rebecca O'Leary for her insightful comments that helped improve the paper.

@@

tab_t %>%
  rowwise() %>%
  mutate(Total = sum(c_across(where(is.numeric)), na.rm = T)) %>%
  arrange(desc(Total)) %>%
  rename(Software = software_used) %>% 
  flextable() %>%
  autofit() %>%
  set_caption(
    "The frequency of use of top ten software programs by year of publication that were found to be used in the papers that were surveyed."
  )
```
